The Implementation of China’s Overseas NGO Law and the Operating Space for International Civil Society

### 2023-09-27 manuscript/manuscript.qmd
Add initial theoretical diagram

```{r libraries-data}
library(tidyverse)
library(scales)
library(lubridate)
library(tidybayes)
library(sf)
library(ggrepel)
library(marginaleffects)
library(patchwork)
library(kableExtra)
library(gt)
library(targets)

@@

```{r fig-ro-ta-pathways, fig.width=6, fig.height=3}
#| echo: false
#| include: true
#| warning: false
#| message: false
#| fig-cap: "Two possible pathways for international NGOs to legally work in 
#|   China, either as formal Registered Organizations (ROs) or by undertaking 
#|   specific Temporary Activities (TAs)"
library(tidygraph)
library(ggraph)

ro_nodes <- tibble(
  step = c(
    "Find a professional supervisory unit (PSU)",
    "Obtain PSU approval",
    "Open organization bank accounts",
    "Keep programming withing approved scope",
    "Submit annual work plans (×2)",
    "Submit annual reports (×2)"
  ),
  type = "Registered organization (RO)"
)
ro_edges <- tibble(from = 1:5, to = 2:6)
ro_graph <- tbl_graph(nodes = ro_nodes, edges = ro_edges)

@@

>>>>

```{r libraries-data}
library(tidyverse)
library(scales)
library(lubridate)
library(tidybayes)
library(sf)
library(ggrepel)
library(marginaleffects)
library(tidygraph)
library(ggraph)
library(patchwork)
library(kableExtra)
library(gt)
library(targets)

@@

```{r fig-ro-ta-pathways, fig.width=6, fig.height=3}
#| echo: false
#| include: true
#| warning: false
#| message: false
#| fig-cap: "Two possible pathways for international NGOs to legally work in 
#|   China, either as formal Registered Organizations (ROs) or by undertaking 
#|   specific Temporary Activities (TAs)"
ro_nodes <- tibble(
  step = c(
    "Find a professional supervisory unit (PSU)",
    "Obtain PSU approval",
    "Open organization bank accounts",
    "Keep programming withing approved scope",
    "Submit annual work plans (×2)",
    "Submit annual reports (×2)"
  ),
  type = "Registered organization (RO)"
)
ro_edges <- tibble(from = 1:5, to = 2:6)
ro_graph <- tbl_graph(nodes = ro_nodes, edges = ro_edges)

@@

See @fig-theory

```{r fig-theory, fig.width=6, fig.height=2}
#| echo: false
#| include: true
#| warning: false
#| message: false
#| fig-cap: "Diagram of our theoretical framework showing three possible determinants of INGO operational flexibility: the contentiousness of the INGO's issue area, the inherent geographic scope of the INGO's operations, and the government's interest in and relationship with the INGO."
theory_nodes <- tribble(
  ~id, ~name, ~x, ~y, ~highlight,
  1,   "Issue contentiousness", 1, 0, FALSE,
  2,   "Operational flexibility", 3, 0, TRUE,
  3,   "Local focus", 2, 1, FALSE,
  4,   "Government relationship and interest", 2, -1, FALSE
)

theory_edges <- tribble(
  ~from, ~to,
  1, 2,
  3, 1,
  3, 2,
  1, 4,
  4, 2
)

theory_graph <- tbl_graph(nodes = theory_nodes, edges = theory_edges)

ggraph(theory_graph, x = x, y = y) + 
  geom_edge_link(
    aes(
      end_cap = label_rect(node2.name, padding = margin(10, 5, 10, 5, "pt"))
    ),
    arrow = arrow(angle = 30, length = unit(6, "pt"), type = "closed"),
    edge_linewidth = 0.25
  ) +
  geom_node_label(
    aes(x = x, y = y, label = name, fill = highlight), 
    size = 3, label.r = unit(0, units = "pt"), fontface = "bold"
  ) +
  scale_x_continuous(expand = expansion(add = 0.3)) +
  scale_y_continuous(expand = expansion(add = 0.2)) +
  scale_fill_manual(values = c("white", clrs[1]), guide = "none") +
  labs(x = NULL, y = NULL) +
  theme_ongo() +
  theme(
    panel.grid.major = element_blank(),
    panel.border = element_blank(),
    axis.text = element_blank(),
  )
```
